Bootstrap Learning via Modular Concept Discovery

### 2013-04-24 drafts/ijcai2013/camera_ready/Dechter.IJCAI13.CameraReady.tex
Removed acknowledgements from title and put them in a separate acknowledgements section at the end of the paper. Added acknowledgement to Google as well.
Minor edits to acknowledgements.
Added Ryan's acknowledgment.

\title{Bootstrap Learning via Modular Concept Discovery\thanks{We acknowledge the support of ARO MURI W911NF-08-1-0242.}}

@@

>>>>

\title{Bootstrap Learning via Modular Concept Discovery}

@@

\section{Acknowledgements}
This work was supported by ARO MURI contract W911NF-08-1-0242 and by a
grant from Google. It was also funded in part by DARPA Young Faculty
Award N66001-12-1-4219.
